Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Discuss blockage ratio in experimental setup; towards #49

The UNH-RVAT turbine has three blades made from NACA 0020 profiles with 0.14 m
chord. The blades are mounted at mid-chord w.r.t. the turbine axis, and the
turbine has a height (blade span) of 1 m and a diameter of 1 m, c.f.
Figure~\ref{fig:turbine}. The rotor has a relatively high solidity $Nc/(\pi D) =
0.13$ and large chord-to-radius ratio $c/R = 0.28$. A CAD model of the turbine
is available from \cite{Bachant2014-RVAT-CAD}.

>>>>

The UNH-RVAT turbine has three blades made from NACA 0020 profiles with 0.14 m
chord. The blades are mounted at mid-chord w.r.t. the turbine axis, and the
turbine has a height (blade span) of 1 m and a diameter of 1 m, c.f.
Figure~\ref{fig:turbine}. The blockage ratio produced by the rotor's frontal
area is 11\%, which we have decided not to correct for, as reliable methods are
not yet agreed upon for CFTs \cite{Cavagnaro2014}. As such, blockage should be
taken into account when using these data for model validation, i.e., the
experimental domain should be mimicked. The rotor has a relatively high solidity
$Nc/(\pi D) = 0.13$ and large chord-to-radius ratio $c/R = 0.28$. A CAD model of
the turbine is available from \cite{Bachant2014-RVAT-CAD}.
